Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2024-12-22 main.tex
editing rel. work section (II-A done)

   First, we focus on HEFT-like scheduling heuristics from the literature  that do not necessarily  
   consider memory constraints. Then, we discuss memory-aware scheduling algorithms. 
   Finally, we move to related work on dynamic or adaptive algorithms. 
 %   \hmey{Question: Does it make sense to place related work before the model (which is more common)?}

@@

    \subsection{Static list schedulers, especially HEFT-based algorithms}

    Introduced in 2002, HEFT~\cite{topcuoglu2002performance} is a list-based heuristic.
    It and all its successors consist of two phases: task prioritization/ordering and task assignment.
    In the first phase, the algorithms compute bottom levels of the tasks based on some priorities (create the list),
    and then schedule tasks in the order of these priorities.
    The modifications of HEFT revolve around the way the priorities of the tasks are computed and the logic of the processor assignment.
    All such algorithms assume a heterogeneous execution environment.

    Hence, during the task prioritization phase in~\cite{sulaiman2021hybrid},  the standard deviation of the computation cost
    (between processors) is computed, and added to the mean value to account for the differences between processor speeds.
    In the processor choice phase, the entry task and the longest parent tasks are duplicated 
    during idle times on the processor.

@@

    PEFT (Predict earliest finish time)~\cite{arabnejad2014list} is a HEFT variant that computes an Optimistic
    Cost Table (OCT).
    The OCT is computed per task-processor pair and stores the longest shortest path from this task to the target task if this
    processor is chosen for this task.
    Ranking is based on OCT values.
    The processor choice stage minimizes the optimistic EFT, which is EFT plus the longest path to the exit node for each task.

    The HSIP (Heterogeneous Scheduling with Improved task Priorities)~\cite{wang2016hsip} has an improved first step in
    comparison to HEFT.
    It combines the standard deviation with the communication cost weight on the tasks.
    In the second stage, the algorithm duplicates the entry task if there is a need for it.

@@

    The SDC algorithm~\cite{SHI2006665} considers the percentage of feasible processors in addition to task’s
    average execution cost in its weight.
    The selected task is then assigned to a processor which minimizes its Adjusted Earliest Finish Time (AEFT) that
    additionally notes how large the communication between current node and its children will be on the
    average provided that it is scheduled on the current processor.

>>>>

First, we focus on HEFT-like scheduling heuristics from the literature  that do not necessarily  
consider memory constraints. Then, we discuss memory-aware scheduling algorithms. 
Finally, we move to related work on dynamic or adaptive algorithms.

@@

\subsection{Static list schedulers, especially HEFT-based algorithms}
\label{sub:static-list-schedulers}
%
Introduced in 2002, HEFT~\cite{topcuoglu2002performance} is a list-based heuristic.
HEFT and its successors consist of two phases: task prio\-ri\-tization/ordering and task assignment.
In the first phase, the algorithms compute bottom levels of the tasks based on some priorities (create the list),
and then schedule tasks in the order of these priorities.
The modifications of HEFT revolve around the way the priorities of the tasks are computed and the logic of the processor assignment.
All such algorithms assume a heterogeneous execution environment.

During the task prioritization phase in~\cite{sulaiman2021hybrid}, the standard deviation of the computation cost % (between processors) 
is computed and added to the mean value to account for differences between processor speeds.
% TODO: Why ``between processors''? And what exactly is ``computation cost'' in the first place?
In the processor choice phase, the entry task and the longest parent tasks are duplicated 
during idle times on the processor.
% TODO: Context of previous sentence unclear. Why is this done? What is the difference to others / our work in this respect?

@@

PEFT (Predict earliest finish time)~\cite{arabnejad2014list} is a HEFT variant that computes an Optimistic
Cost Table (OCT).
The OCT is computed per task-processor pair and stores the longest shortest path from this task to the target task if this
processor is chosen for this task.
% TODO: is ``target task'' defined/clear?
Ranking is based on OCT values.
The processor choice stage minimizes the optimistic EFT, which is EFT plus the longest path to the exit node for each task. % TODO: is ``exit node'' == ``target task''?

The HSIP (Heterogeneous Scheduling with Improved task Priorities)~\cite{wang2016hsip} has an improved first step in
comparison to HEFT.
It combines the standard deviation with the communication cost weight on the tasks.
In the second stage, the algorithm duplicates the entry task if there is a need for it.
% TODO: Sounds like Ref. [32] above. What is the difference? (Why) Is it an improvement? Do we need to describe both?

@@

The SDC algorithm~\cite{SHI2006665} considers the percentage of feasible processors in addition to a task’s
average execution cost in its weight.
The selected task is then assigned to a processor which minimizes its Adjusted Earliest Finish Time (AEFT),
which additionally notes how large the communication between the current node and its children will be on 
average when scheduled on the current processor.
